A Recipe for Scavenging \textcolor{blue}{in Vertebrates} - the natural history of a behaviour

### 2016-07-13 response_letter.tex

\documentclass{letter}
%\signature{Your name}
%\address{Street \\ City \\ Country}
\begin{document}
\begin{letter}{Company name \\ Street\\ City\\ Country}
\opening{To the editor}

We would like to thank the editor, subject editor and reviewers for their comments. By bringing attention to elements of the manuscript that require more careful communication we believe that you have helped us to significantly improve our manuscript. In this submission we have clarified these areas and added a body of work to bolster the conclusions drawn from our work. Please see below where we consider each of your points in turn.

Reviewer: 1

Comments to the Author
This paper attempts to synthesize literature on traits that enable scavenging behavior in extant and extinct vertebrates.  The paper is mostly well written, and most (but not all) pertinent literature sources are included.  I do worry about the lack of novelty of the manuscript, and what I perceived as haphazard organization.  Here are some specific issues that should be addressed in my opinion:

1.      Abstract:  Scavenging can be difficult to observe, but probably no more so than predation.  Also, using experimental carcasses, scavenging is actually quite easy to observe.

2.      Abstract:  You should point out that your ‘scale of scavenging’ is only qualitative; you made no attempt to quantify such traits.

3.      Introduction:  Much of this section seems to follow DeVault’s (2003) review paper on scavenging—in fact, there is almost nothing new here that is not covered in that earlier review.

4.      Introduction:  You mention that you will use “other methods in order to discern the most suitable morphologies…”  but you don’t say what they are.  What other methods are you talking about?

5.      I think that early on in the paper you need to define obligate and facultative scavengers and then throughout the paper, specify which you are referring to.  For example, in the first sentence of the Detection section, you talk about ‘known scavengers’, but it is unclear if you really mean obligate scavengers.  Nearly all carnivorous vertebrates are scavengers at least to some extent, so you need to elaborate on what you mean when you talk about ‘scavengers’.

6.      Last sentence of Introduction:  Again, you propose a ‘scale of scavenging’, but without quantification, it is unclear how useful this ‘scale’ is.

7.      Page 6, 12:  In your discussion of aquatic scavengers, you might want to refer to Beasley et al. (2012; Oikos 121:1021-1026).

8.      Page 6:  Why is jaw morphology likely to define scavengers?  Please elaborate.

9.      Page 9:  It is true that carrion can comprise a large percentage of a hyena’s diet, but your text seems misleading.  Most studies have shown that most of a hyena’s diet is from predation.  For example, see Cooper et al. (1999; Afr. J. Ecol. 37:149–160) and Gasaway et al. (1991; Afr. J. Ecol. 29: 64–75).
Reviewer: 1

Comments to the Author
This paper attempts to synthesize literature on traits that enable scavenging behavior in extant and extinct vertebrates.  The paper is mostly well written, and most (but not all) pertinent literature sources are included.  I do worry about the lack of novelty of the manuscript, and what I perceived as haphazard organization.  Here are some specific issues that should be addressed in my opinion:

1.      Abstract:  Scavenging can be difficult to observe, but probably no more so than predation.  Also, using experimental carcasses, scavenging is actually quite easy to observe.
2.      Abstract:  You should point out that your ‘scale of scavenging’ is only qualitative; you made no attempt to quantify such traits.
3.      Introduction:  Much of this section seems to follow DeVault’s (2003) review paper on scavenging—in fact, there is almost nothing new here that is not covered in that earlier review.
4.      Introduction:  You mention that you will use “other methods in order to discern the most suitable morphologies…”  but you don’t say what they are.  What other methods are you talking about?
5.      I think that early on in the paper you need to define obligate and facultative scavengers and then throughout the paper, specify which you are referring to.  For example, in the first sentence of the Detection section, you talk about ‘known scavengers’, but it is unclear if you really mean obligate scavengers.  Nearly all carnivorous vertebrates are scavengers at least to some extent, so you need to elaborate on what you mean when you talk about ‘scavengers’.
6.      Last sentence of Introduction:  Again, you propose a ‘scale of scavenging’, but without quantification, it is unclear how useful this ‘scale’ is.
7.      Page 6, 12:  In your discussion of aquatic scavengers, you might want to refer to Beasley et al. (2012; Oikos 121:1021-1026).
8.      Page 6:  Why is jaw morphology likely to define scavengers?  Please elaborate.
9.      Page 9:  It is true that carrion can comprise a large percentage of a hyena’s diet, but your text seems misleading.  Most studies have shown that most of a hyena’s diet is from predation.  For example, see Cooper et al. (1999; Afr. J. Ecol. 37:149–160) and Gasaway et al. (1991; Afr. J. Ecol. 29: 64–75).
10.     Your section on Handling Time is so short that I think it should be cut or combined with another section.

Reviewer: 2

Comments to the Author
This article is a review of the literature what the authors term a "natural history" of scavenging. They have approached the topic from the perspective of ecological variables (and other variables that condition them) in optimal foraging theory including encounter rate and handling time, but also metabolism, locomotion (e.g soaring and swimming), detection, prey availability, competition, and food processing. They describe many useful examples of the behavior and ecology of obligate and facultative scavengers. But I think they often go to far in their assumptions in trying to weave these examples together in a synthetic way. Some examples are inferring scrounging behaviors in flying pterosaurs (pace 11), assuming that hominins used vultures to identify scavenging opportunities (page 11), surmising that scavenging evolved with the earliest tetrapods based on "potential carrion unexploited by marine vertebrates" (page 12). There is a lot of "these researchers have suggested X" and then taking that as a given fact.

While the authors distinguish between obligate and facultative scavenging, they tend to lump them together when it comes to constructing their arguments. In the end, is the argument about the former, or the latter? Is the real interest in whether species scavenge at all, what proportion of their resources are obtained by scavenging, or what the conditions are that produce facultative or obligate scavengers? They also seem to ignore flexibility in species' behaviors. For instance, while spotted hyenas are on their highly scavenging side of their Figures 1 and 2, in some ecosystems they hunt significant proportion of their prey. Similarly, lions can take a large proportion of their prey as scavenged, as the authors note. But to suggest, as they do in their abstract, that they can apply their scale of scavenging to any species at any time to judge how important scavenging was in its diet is frankly completely ignoring behavioral variability over time and space. It is substantially more difficult with fossil species for which we may know far fewer of the variables they list in Figure 1, in a nuanced way. Figure 2 does not display the diversity of scavengers through time, it displays examples of species that display observed or inferred scavenging behaviors. Diversity has specific ecological definition(s) that are being ignored here.

If the authors chose to resubmit, I would suggest they organize their manuscript based on known information about modern species, known (e.g. bone processing by theropods) and inferred (e.g. scavenging in hominins) information about fossil species, and then try to draw broader conclusions. They might look to articles about other modern scavenging opportunities such as Capaldo and Peter's study of wildebeest drownings http://www.sciencedirect.com/science/article/pii/S0305440385700398, and suggestions that sabertooth cats which they claim were unable to feed on bones may have consumed more bone than penecontemporaneous dire wolves https://www.jstor.org/stable/20627167?seq=1#page_scan_tab_contents.

In sum, while I think the aim of the article is a very worthwhile one, I think the authors cannot claim to have produced an all-encompassing model that can predict the presence or level of scavenging in any organism - because I think this simply cannot be done.

Finally, some of the perspectives of this manuscript overlap substantially with parts of Beasley et al. 2015 (pages 108-112), which is cited numerous times in the manuscript.
10.     Your section on Handling Time is so short that I think it should be cut or combined with another section.

Reviewer: 2

Comments to the Author
This article is a review of the literature what the authors term a "natural history" of scavenging. They have approached the topic from the perspective of ecological variables (and other variables that condition them) in optimal foraging theory including encounter rate and handling time, but also metabolism, locomotion (e.g soaring and swimming), detection, prey availability, competition, and food processing. They describe many useful examples of the behavior and ecology of obligate and facultative scavengers. But I think they often go to far in their assumptions in trying to weave these examples together in a synthetic way. Some examples are inferring scrounging behaviors in flying pterosaurs (pace 11), assuming that hominins used vultures to identify scavenging opportunities (page 11), surmising that scavenging evolved with the earliest tetrapods based on "potential carrion unexploited by marine vertebrates" (page 12). There is a lot of "these researchers have suggested X" and then taking that as a given fact.

While the authors distinguish between obligate and facultative scavenging, they tend to lump them together when it comes to constructing their arguments. In the end, is the argument about the former, or the latter? Is the real interest in whether species scavenge at all, what proportion of their resources are obtained by scavenging, or what the conditions are that produce facultative or obligate scavengers? They also seem to ignore flexibility in species' behaviors. For instance, while spotted hyenas are on their highly scavenging side of their Figures 1 and 2, in some ecosystems they hunt significant proportion of their prey. Similarly, lions can take a large proportion of their prey as scavenged, as the authors note. But to suggest, as they do in their abstract, that they can apply their scale of scavenging to any species at any time to judge how important scavenging was in its diet is frankly completely ignoring behavioral variability over time and space. It is substantially more difficult with fossil species for which we may know far fewer of the variables they list in Figure 1, in a nuanced way. Figure 2 does not display the diversity of scavengers through time, it displays examples of species that display observed or inferred scavenging behaviors. Diversity has specific ecological definition(s) that are being ignored here.

If the authors chose to resubmit, I would suggest they organize their manuscript based on known information about modern species, known (e.g. bone processing by theropods) and inferred (e.g. scavenging in hominins) information about fossil species, and then try to draw broader conclusions. They might look to articles about other modern scavenging opportunities such as Capaldo and Peter's study of wildebeest drownings http://www.sciencedirect.com/science/article/pii/S0305440385700398, and suggestions that sabertooth cats which they claim were unable to feed on bones may have consumed more bone than penecontemporaneous dire wolves

In sum, while I think the aim of the article is a very worthwhile one, I think the authors cannot claim to have produced an all-encompassing model that can predict the presence or level of scavenging in any organism - because I think this simply cannot be done.

Finally, some of the perspectives of this manuscript overlap substantially with parts of Beasley et al. 2015 (pages 108-112), which is cited numerous times in the manuscript.

### 2016-07-13 natural history of scavenging.tex
Response and manuscript formatted for response

\documentclass[a4paper,12pt]{article}
\usepackage{ecography}
\usepackage{lmodern}
\usepackage{amsmath}
\usepackage{xfrac}
\usepackage{lineno}

@@

\title{A Recipe for Scavenging in Vertebrates - the natural history of a behaviour}

@@

\begin{abstract} 
Despite its prevalence, scavenging is a difficult behaviour to observe in modern day carnivores and impossible to study directly in extinct species. 
Yet, there are certain intrinsic and environmental features of a species that push it towards a scavenging lifestyle. 
These can be thought of as some of the principal parameters in optimal foraging theory namely, encounter rate, handling time and prey availability. 
We use these components to highlight the morphologies and environments that would have been conducive to scavenging over geological time by focusing on the dominant vertebrate groups of the land, sea and air. 
The result is a synthesis on the natural history of scavenging. 
Our idea of a scale of scavenging can be applied to any species at any time to help judge the importance of this behaviour in its diet. 
\end{abstract}

@@

Historically, food webs have classified most acts of carnivory as predation events \citep{wilson2011scavenging}. 
This is clearly a mistaken view because of the existence of scavenging, a behaviour displayed by almost all carnivorous vertebrates \citep{devault2003scavenging}. 
Recent research has begun to redress this imbalance by recognising the prevalence of scavenging and detailing its ecological consequences across modern ecosystems where we are beginning to appreciate the implications for the trophic ecology of these systems \citep{pereira2014facultative,periquet2015lion}.
Indeed, there is no discrete divide between predators and scavengers but rather a continuous gradient \citep{pereira2014facultative}.
Unfortunately, the lack of direct behavioural data makes it difficult to discern scavenging from predation among extinct forms where it was surely exhibited to a similar extent among prehistoric vertebrate carnivores.
Some simple heuristics can inform us whether or not the prey was scavenged, for instance, in cases where it was simply too large to have been killed by the ostensible predator \citep{pobiner2008paleoecological}.
But clearly, a scavenger does not only feed on animals too big for it to have hunted.
There are other methods however, that allow us to discern the most suitable morphologies, physiologies and environments for a scavenging lifestyle to prosper e.g. energetics models, comparative anatomy, palaeontology etc. \citep{shipman1986scavenging,ruxton2003could}. 
Yet, a synthesis describing the natural history of scavengers is absent from the literature.
Here we rectify this shortcoming in charting the natural history of scavenging by assessing its potential among extinct vertebrate groups given their ecology, functional traits and the enviornmental context.

@@

Species that rely on scavenging to sustain substantial portions of their diets must encounter a sufficient amount of carrion in order to meet their energetic demands.
Once found, the scavenger must be able to out-compete any potential competitors and efficiently process the, typically decaying, carcass replete with micro-organism derived toxins \citep{ruxton2014fruit}. 
These characteristics can be assumed to be under evolutionary selection pressures for traits that increase carrion discovery and monopoly.
Finally, the potential for scavenging will also depend on the density, size, and quality of carcases produced, all of which are affected by complex ecosystem dynamics \citep{moleon2014inter}. 
Even these aspects can be indirectly impacted by the behaviour of the scavenger \citep{moleon2014inter}.
Each of these facets are essentially the backbone of fundamental ecological theory and are the key parameters defined in functional response curves, namely encounter rate, handling time and prey availability \citep{jeschke2002predator}.  
By considering scavenging in this context of optimal foraging we can identify the prerequisite attributes and processes required for the behaviour. 
This has enabled us to propose a scale of scavenging whereupon we can place an extinct vertebrate carnivore and assess the likely importance of carrion in its diet.

@@

\section{Encounter Rate}
All foraging processes depend on the encounter rate between consumer and resource. 
Locomotory speed, foraging time and detection radius all determine the encounter rate between a scavenger and the carcasses it is searching for and we would thus expect selection pressures to act on the various traits that govern these parameters.
Selection might also drive a species to reduce its metabolic requirements so that it can survive long periods between meals, or expand a species ability to process tissues or decaying flesh that might ordinarily be discarded.
However, as we noted above, encounter rate is also determined by the productivity of the environment, and ultimately the rate at which carcasses are produced. 
Scavengers can drive this process indirectly, for instance, by consuming the majority of carrion, obligate scavengers deny a resource to their facultative counterparts obliging the latter to hunt more and thus produce more carrion \citep{moleon2014inter}.

@@

\subsection{Locomotion}
The relative unpredictability of carrion also means scavenging depends more on the ability to efficiently move over larger areas than does predation.
This generally requires an efficient transfer of metabolic energy into movement which relies on the animal's anatomy and physiology as well as the medium of the environment in which the animal is moving (i.e. aerial, aquatic or terrestrial).
Perhaps the most efficient form of locomotion in vertebrates is found in flying species. 
Despite the energetic costs of flight, the only known vertebrate obligate scavengers are the old and the new world vultures. 
While powered flight is energetically expensive, species like vultures have evolved behavioural and anatomical features to exploit air currents using their large wingspans, allowing them to soar at a cost of only twice their metabolic rate \citep{hedenstrom1993migration,spivey2014analysing}.
By depending on thermal air flows these species can forage over vast ranges \citep{spiegel2013factors}. 
An analogous mode of locomotion is also exploited by seabirds, who use strong ocean winds to search large areas of the oceans \citep{norberg2012vertebrate,thaxter2012seabird}. 
While many species of seabird are likely primarily predators, it seems that albatrosses, who can range many hundreds of kilometres, take a substantial amount of carrion in their diet \citep{croxall1994dead}. 
This is typically in the form of squid carcases, which float on the surface, allowing the birds to readily pluck their remains out of the water \citep{croxall1994dead}.

@@

We know that many extant birds exist as facultative scavengers because storks, raptors and corvids all take substantial quantities of carrion in their diet \citep{mateo2015regional}. 
Similarly we would expect that extinct species would also scavenge in a similar fashion depending on the efficiency of their flight. 
For example, early birds such as \textit{Archaeopteryx} are predicted to have been poor, relatively inefficient fliers \citep{nudds2010narrow} and so ill-suited to finding carrion. 
The importance of efficient flying over large areas may explain the lack of scavenging behaviour in bats as they are generally nocturnal, a time when they would receive no aid from convective air currents \citep{norberg2012vertebrate}.

@@

Whatever the case, it is with the evolution of endothermy in the therapsid-mammal lineage \citep{clarke2010temperature} that terrestrial vertebrates would have gained the ability to range more widely, a vital component in seeking out carrion.
Modern endothermic mammals can sustain longer periods of energetically expensive activity \citep{bennett1979endothermy} resulting in larger foraging ranges. 
Today, terrestrial scavenging in the mammals is probably best known in the species rich African context where hyenas, jackals and lions all take sizeable proportions of carrion in their diet \citep{pereira2014facultative,periquet2015lion}.
In the spotted hyena (\textit{Crocuta crocuta}), striped hyena (\textit{Hyaena hyaena}) and brown hyena (\textit{Hyaena brunnea}) it can be over 90\% \citep{jones2015african}.
And although no contemporary terrestrial vertebrate exists as an obligate scavenger, most, if not all, are facultative to some extent \citep{devault2003scavenging,beasley2015vertebrates,pereira2014facultative}.
The particular reliance of hyenas on carrion means we can use them as examples of efficient terrestrial scavengers to compare with other forms \citep{periquet2015lion}. 
In terms of locomotion, they employ a characteristic ``rocking horse gait"  which allows them to cover great distances efficiently, loping at 10 km/hr \citep{mills1989comparative,jones2015african}. 
Such long-distance travel is apparent many other cursorial predators \citep{pennycuick1995radius,janis2014forelimb,pereira2014facultative}. 
In contrast, big cats rely on ambush \citep{pennycuick1995radius,pereira2014facultative}. 
This difference means ambush predators tend to be more obligate hunters \citep{pereira2014facultative} 
These insights allow us to compare extant terrestrial species to their prehistoric forebears given the dominance of mammalian carnviores since the Eocene (56-33.9 Mya) where the order split into the Caniforma and Feliforma \citep{van1987skeletal}.
To take one example, \cite{anyonge1996locomotor} found that \textit{Nimravides}, a genus of sabretooth cat from the Miocence (10.3 - 5.3 Mya), were likely to have been ambush predators which would argue against them taking a lot of carrion.

Of course, terrestrial animals can also move bipedally. 
Although the evolution of bipedal movement was significant in that it freed up the forelimbs for other purposes (e.g. climbing, tool-use, wing development etc.) it does not differ radically in cost from quadrupedal locomotion (\cite{williams1999evolution}, and references therein). 
For instance, \cite{alexander2004bipedal} shows that, in the case of humans, we are more economical than predicted while walking and less so while running according to predicted costs of terrestrial movement calculated by allometric scaling relationships.
Our locomotory efficiency has fed into the question of where our ancestors placed on the hunter-scavenger axis during the Plio-Pleistocene, which has been a matter of debate for years \citep{dominguez2002hunting}.
\cite{ruxton2013endurance} added to this debate with their argument that long distance endurance running was not an important feature of hominin scavenging but was instead used by humans for hunting.
Even when considering the use of weapons and social foraging, the authors argue that the high costs of running long distances would render it an unattractive foraging strategy for scavenging.

@@

\subsection{Sensory Detection}

@@

Existing in this environment also means being able to gather a wealth of information from other foragers, be they conspecifics or otherwise \citep{jackson2008effect,KaneVul,moleon2014inter}.
These interactions are properly three dimensional in the sense of \cite{pawar2012dimensionality} because both producer and scrounger are in the air \citep{dall2005information}. 
Again, returning to vultures, the genus \textit{Gyps} consists of highly social and colonially nesting species \citep{fernandez2015density}.
These behaviours allow them to forage far more efficiently because one bird can scrounge information on the location of food from another successful forager \citep{cortes2014bird}.
Information transfer of this kind is typically inadvertent and as a consequence no complex social interactions are required, simply the ability to recognise a successful forager.
Thus, it seems probable that scrounging behaviours were seen in the flying pterosaurs as well.

@@

\subsection{Carcass Availability}
The environmental influence on carcass availability is an aspect that greatly affects encounter rate. %but is invisible to the selective forces acting on the scavenger. 
Aspects including, primary productivity, relief, and temperature will all affect scavenging tendency. 
\cite{ruxton2004obligate} suggest an historic ecosystem with a productivity similar to the Serengeti could have supported an \textit{obligate} mammalian or reptilian terrestrial scavenger.
Indeed, in systems that were dominated by large ectothermic or mesothermic herbivore vertebrates, the same primary productivity would have supported a greater biomass, due to the scaling of mass with metabolic rate \citep{mcnab2009resources}.
The upshot of this may have been a higher biomass of herbivores dying and offering scavenging opportunities (although these larger species may have also lived longer).

@@

The physical differences between water and air mean carcass availability is radically different between these environments \citep{beasley2012carrion}. 
For one, carcasses get moved around by water which results in a more diffuse signal being produced for would-be scavengers.
Carcasses also tend to sink in water where they are no longer accessible to pelagic scavengers \citep{beasley2012carrion}. 
Research has shown that an animal need only travel between 16 to 36 km to encounter a fresh whale carcass \citep{moleon2015living}. 
The phenomenon of occasional bounties of carrion in the form of these whale falls has led some researchers to investigate if an obligate scavenger could survive by seeking out these remains exclusively.
\cite{ruxton2005searching} argued that although this is energetically feasible it's ecologically unlikely.
Any animal that could find such whale carcasses is unlikely to have ignored other types of carrion.
Although no aquatic species have ever exceeded the size of whales, some enormous animals have evolved in this environment before the evolution of cetaceans, including \textit{Leedsichthys}, a bony fish from the Middle Jurassic (174.1 - 163.5 Mya) and the aquatic Mesozoic reptiles, the plesiosaurs, pliosaurs and ichtyosaurs, that could all exceed 15 metres in length \citep{ruxton2011zoology,danise2014ecological}.
So, despite being unlikely, the energetic feasibility of a marine scavenger that specialises on large carcasses has a long history.

@@

\subsection{Competition}
Large body size has substantial advantages in agonistic interactions \citep{ruxton2004obligate,moleon2014inter,pereira2014facultative}. 
For instance, lions can acquire much of their carrion through kleptoparasitism of hyena kills \citep{trinkel2005competitive,pereira2014facultative,periquet2015lion}. 
This line of reasoning suggests that some theropod dinosaurs, who could get up to 15 tonnes, would have had easily monopolised a carcass \citep{weishampel2004dinosauria} provided they could find them efficiently \citep{kane2016body}.

>>>>

\documentclass[a4paper,12pt]{article}
\usepackage{ecography}
\usepackage{lmodern}
\usepackage{amsmath}
\usepackage{xfrac}
\usepackage{lineno}
\usepackage{color}

@@

\title{A Recipe for Scavenging \textcolor{blue}{in Vertebrates} - the natural history of a behaviour}

@@

\begin{abstract} 
Despite its prevalence, scavenging is a difficult behaviour to observe in modern day carnivores and impossible to study directly in extinct species. 
Yet, there are certain intrinsic and environmental features of a species that push it towards a scavenging lifestyle. 
These can be thought of as some of the principal parameters in optimal foraging theory namely, encounter rate, handling time and prey availability. 
We use these components to highlight the morphologies and environments that would have been conducive to scavenging over geological time by focusing on the dominant vertebrate groups of the land, sea and air. 
The result is a synthesis on the natural history of scavenging. 
Our idea of a scale of scavenging can be applied to any species at any time to help \textcolor{blue}{judge} the importance of this behaviour in its diet. 
\end{abstract}

@@

Historically, \textcolor{blue}{food webs have classified most acts of carnivory as predation events \citep{wilson2011scavenging}. 
This is clearly a mistaken view because of the existence of scavenging, a behaviour displayed by almost all carnivorous vertebrates \citep{devault2003scavenging}. 
Recent research has begun to redress this imbalance by recognising the prevalence of scavenging and detailing its ecological consequences across modern ecosystems where we are beginning to appreciate the implications for the trophic ecology of these systems \citep{pereira2014facultative,periquet2015lion}.
Indeed, there is no discrete divide between predators and scavengers but rather a continuous gradient \citep{pereira2014facultative}.
Unfortunately, the lack of direct behavioural data makes it difficult to discern scavenging from predation among extinct forms where it was surely exhibited to a similar extent among prehistoric vertebrate carnivores.
Some simple heuristics can inform us whether or not the prey was scavenged, for instance, in cases where it was simply too large to have been killed by the ostensible predator \citep{pobiner2008paleoecological}.}
But clearly, a scavenger does not only feed on animals too big for it to have hunted.
\textcolor{blue}{There are other methods however, that allow us to discern the most suitable morphologies, physiologies and environments for a scavenging lifestyle to prosper e.g. energetics models, comparative anatomy, palaeontology etc. \citep{shipman1986scavenging,ruxton2003could}. 
Yet, a synthesis describing the natural history of scavengers is absent from the literature.
Here we rectify this shortcoming in charting the natural history of scavenging by assessing its potential among extinct vertebrate groups given their ecology, functional traits and the environmental context.}

@@

\textcolor{blue}{Species that rely on scavenging to sustain substantial portions of their diets must encounter a sufficient amount of carrion in order to meet their energetic demands.
Once found, the scavenger must be able to out-compete any potential competitors and efficiently process the, typically decaying, carcass replete with micro-organism derived toxins \citep{ruxton2014fruit}.}
These characteristics can be assumed to be under evolutionary selection pressures for traits that increase carrion discovery and monopoly.
Finally, the potential for scavenging will also depend on the density, size, and quality of carcases produced, all of which are affected by complex ecosystem dynamics \textcolor{blue}{\citep{moleon2014inter}. 
Even these aspects can be indirectly impacted by the behaviour of the scavenger \citep{moleon2014inter}.}
Each of these facets are essentially the backbone of fundamental ecological theory and are the key parameters defined in functional response curves, namely encounter rate, handling time and prey availability \citep{jeschke2002predator}.  
By considering scavenging in this context of optimal foraging we can identify the prerequisite attributes and processes required for the behaviour. 
This has enabled us to propose a scale of scavenging whereupon we can place \textcolor{blue}{an extinct vertebrate carnivore} and assess the likely importance of carrion in its diet.

@@

\section{Encounter Rate}
All foraging processes depend on the encounter rate between consumer and resource. 
Locomotory speed, foraging time and detection radius all determine the encounter rate between a scavenger and the carcasses it is searching for and we would thus expect selection pressures to act on the various traits that govern these parameters.
Selection might also drive a species to reduce its metabolic requirements so that it can survive long periods between meals, or expand a species ability to process tissues or decaying flesh that might ordinarily be discarded.
However, as we noted above, encounter rate is also determined by the productivity of the environment, and ultimately the rate at which carcasses are produced. 
\textcolor{blue}{Scavengers can drive this process indirectly, for instance, by consuming the majority of carrion, obligate scavengers deny a resource to their facultative counterparts obliging the latter to hunt more and thus produce more carrion \citep{moleon2014inter}.}

@@

\subsection{Locomotion}
The \textcolor{blue}{relative} unpredictability of carrion also means scavenging depends more on the ability to efficiently move over larger areas than does predation.
This generally requires an efficient transfer of metabolic energy into movement which relies on the animal's anatomy and physiology as well as the medium of the environment in which the animal is moving (i.e. aerial, aquatic or terrestrial).
Perhaps the most efficient form of locomotion in vertebrates is found in flying species. 
Despite the energetic costs of flight, the only known vertebrate obligate scavengers are the old and the new world vultures. 
While powered flight is energetically expensive, species like vultures have evolved behavioural and anatomical features to exploit air currents using their large wingspans, allowing them to soar at a cost of only twice their metabolic rate \citep{hedenstrom1993migration,spivey2014analysing}.
By depending on thermal air flows these species can forage over vast ranges \citep{spiegel2013factors}. 
An analogous mode of locomotion is also exploited by seabirds, who use strong ocean winds to search large areas of the oceans \citep{norberg2012vertebrate,thaxter2012seabird}. 
While many species of seabird are likely primarily predators, it seems that albatrosses, who can range many hundreds of kilometres, take a substantial amount of carrion in their diet \citep{croxall1994dead}. 
This is typically in the form of squid carcases, which float on the surface, allowing the birds to readily pluck their remains out of the water \citep{croxall1994dead}.

@@

We know that many extant birds exist as facultative scavengers because storks, raptors and corvids all take substantial quantities of carrion in their diet \textcolor{blue}{\citep{mateo2015regional}}. 
Similarly we would expect that extinct species would also scavenge in a similar fashion depending on the efficiency of their flight. 
For example, early birds such as \textit{Archaeopteryx} are predicted to have been poor, relatively inefficient fliers \citep{nudds2010narrow} and so ill-suited to finding carrion. 
The importance of efficient flying over large areas may explain the lack of scavenging behaviour in bats as they are generally nocturnal, a time when they would receive no aid from convective air currents \citep{norberg2012vertebrate}.

@@

Whatever the case, it is with the evolution of endothermy in the therapsid-mammal lineage \citep{clarke2010temperature} that terrestrial vertebrates would have gained the ability to range more widely, a vital component in seeking out carrion.
Modern endothermic mammals can sustain longer periods of energetically expensive activity \citep{bennett1979endothermy} resulting in larger foraging ranges. 
Today, terrestrial scavenging in mammals is probably best known in the African Savannah context where hyenas, jackals and lions all take sizeable proportions of carrion in their diet \textcolor{blue}{\citep{pereira2014facultative,periquet2015lion}.}
In the spotted hyena (\textit{Crocuta crocuta}), striped hyena (\textit{Hyaena hyaena}) and brown hyena (\textit{Hyaena brunnea}) it can be over 90\% \citep{jones2015african}.
And although no contemporary terrestrial vertebrate exists as an obligate scavenger, most, if not all, are facultative to some extent \textcolor{blue}{\citep{devault2003scavenging,beasley2015vertebrates,pereira2014facultative}}.
The particular reliance of hyenas on carrion means we can use them as examples of efficient terrestrial scavengers to compare with other forms \textcolor{blue}{\citep{periquet2015lion}}. 
In terms of locomotion, they employ a characteristic ``rocking horse gait''  which allows them to cover great distances efficiently, loping at 10 km/hr \citep{mills1989comparative,jones2015african}. 
Such long-distance travel is apparent \textcolor{blue}{in many other cursorial predators \citep{pennycuick1995radius,janis2014forelimb,pereira2014facultative}}. 
In contrast, big cats rely on ambush \citep{pennycuick1995radius,pereira2014facultative}. 
This difference means ambush predators tend to be more obligate hunters \citep{pereira2014facultative} 
These insights allow us to compare extant terrestrial species to their prehistoric forebears given the dominance of mammalian carnviores since the Eocene (56-33.9 Mya) where the order split into the Caniforma and Feliforma \citep{van1987skeletal}.
To take one example, \cite{anyonge1996locomotor} found that \textit{Nimravides}, a genus of sabretooth cat from the Miocence (10.3 - 5.3 Mya), were likely to have been ambush predators which would argue against them taking a lot of carrion.

Of course, terrestrial animals can also move bipedally. 
Although the evolution of bipedal movement was significant in that it freed up the forelimbs for other purposes (e.g. climbing, tool-use, wing development etc.) it does not differ radically in cost from quadrupedal locomotion (\cite{williams1999evolution}, and references therein). 
For instance, \cite{alexander2004bipedal} shows that, in the case of humans, we are more economical than predicted while walking and less so while running according to predicted costs of terrestrial movement calculated by allometric scaling relationships.
Our locomotory efficiency has fed into the question of where our ancestors placed on the hunter-scavenger axis during the Plio-Pleistocene, which has been a matter of debate for years \citep{dominguez2002hunting}.
\cite{ruxton2013endurance} added to this debate with their argument that long distance endurance running \textcolor{blue}{was not an important feature of hominin scavenging but was instead used by humans for hunting.
Even when considering the use of weapons and social foraging, the authors argue that the high costs of running long distances would render it an unattractive foraging strategy for scavenging.}

@@

\subsection{\textcolor{blue}{Sensory} Detection}

@@

Existing in this environment also means being able to gather a wealth of information from other foragers, be they conspecifics or otherwise \textcolor{blue}{\citep{jackson2008effect,KaneVul,moleon2014inter}}.
These interactions are properly three dimensional in the sense of \cite{pawar2012dimensionality} because both producer and scrounger are in the air \citep{dall2005information}. 
Again, returning to vultures, the genus \textit{Gyps} consists of highly social and colonially nesting species \citep{fernandez2015density}.
These behaviours allow them to forage far more efficiently because one bird can scrounge information on the location of food from another successful forager \textcolor{blue}{\citep{cortes2014bird}}.
Information transfer of this kind is typically inadvertent and as a consequence no complex social interactions are required, simply the ability to recognise a successful forager.
Thus, it seems probable that scrounging behaviours were seen in the flying pterosaurs as well.

@@

\subsection{\textcolor{blue}{Carcass} Availability}
The environmental influence on \textcolor{blue}{carcass} availability is an aspect that greatly affects encounter rate. %but is invisible to the selective forces acting on the scavenger. 
Aspects including, primary productivity, relief, and temperature will all affect scavenging tendency. 
\cite{ruxton2004obligate} suggest an historic ecosystem with a productivity similar to the Serengeti could have supported an \textit{obligate} mammalian or reptilian terrestrial scavenger.
Indeed, in systems that were dominated by large ectothermic or mesothermic herbivore vertebrates, the same primary productivity would have supported a greater biomass, due to the scaling of mass with metabolic rate \citep{mcnab2009resources}.
The upshot of this may have been a higher biomass of herbivores dying and offering scavenging opportunities (although these larger species may have also lived longer).

@@

\textcolor{blue}{The physical differences between water and air mean carcass availability is radically different between these environments \citep{beasley2012carrion}. 
For one, carcasses get moved around by water which results in a more diffuse signal being produced for would-be scavengers.
Carcasses also tend to sink in water where they are no longer accessible to pelagic scavengers \citep{beasley2012carrion}. 
Research has shown that an animal need only travel between 16 to 36 km to encounter a fresh whale carcass \citep{moleon2015living}. 
The phenomenon of occasional bounties of carrion in the form of these whale falls has led some researchers to investigate if an obligate scavenger could survive by seeking out these remains exclusively.}
\cite{ruxton2005searching} argued that although this is energetically feasible it's ecologically unlikely.
Any animal that could find such whale carcasses is unlikely to have ignored other types of carrion.
Although no aquatic species have ever exceeded the size of whales, some enormous animals have evolved in this environment before the evolution of cetaceans, including \textit{Leedsichthys}, a bony fish from the Middle Jurassic (174.1 - 163.5 Mya) and the aquatic Mesozoic reptiles, the plesiosaurs, pliosaurs and ichtyosaurs, that could all exceed 15 metres in length \citep{ruxton2011zoology,danise2014ecological}.
So, despite being unlikely, the energetic feasibility of a marine scavenger that specialises on large carcasses has a long history.

@@

\subsection{Competition}
Large body size has substantial advantages in agonistic interactions \textcolor{blue}{\citep{ruxton2004obligate,moleon2014inter,pereira2014facultative}}. 
For instance, lions can acquire much of their carrion through kleptoparasitism of hyena kills \textcolor{blue}{\citep{trinkel2005competitive,pereira2014facultative,periquet2015lion}}. 
This line of reasoning suggests that some theropod dinosaurs, who could get up to 15 tonnes, would have had easily monopolised a carcass \citep{weishampel2004dinosauria} provided they could find them efficiently \citep{kane2016body}.

We would expect this trait to be selected for even in the case of weight-constrained, scavenging fliers.
This is true for \textcolor{blue}{many vultures and other major avian scavengers such as albatrosses who can have body masses in excess of} 10 kg and represent some of the heaviest bird species capable of flight \citep{weimerskirch1992reproductive,ferguson2001raptors,donazar2002effects}.
Indeed, such is the competitive advantage held by vultures over other facultative scavenging birds that temporal niche partitioning at the carcass has evolved \textcolor{blue}{\citep{kendall2013alternative,KaneVul,moreno2016behavioral}}. 
Additionally, many pterosaurs were far bigger again, with estimated body masses of over 200 kg in the Azhdarchids \citep{witton2010size}.
Although \cite{witton2008reappraisal} argued that neck inflexibility and straight, rather than hooked jaw morphology points against Azhdarchids existing as \textit{obligate} scavengers, their terrestrial proficiency indicates they would have been comfortable foraging on the ground.
Extant Marabou Storks (\textit{Leptoptilos crumenifer}) have a comparable morphology and are noted facultative scavengers \citep{monadjem2012survival} so it is reasonable to believe that these pterosaurs behaved similarly.
